Sparse spectral methods for partial differential equations on spherical caps

### 2021-05-04 papers/spherical-caps/revised/response-to-referees.tex

\thispagestyle{empty}

\hfill
\begin{flushright}
Correspondence to: \\
Sheehan Olver \\
s.olver@imperial.ac.uk \\
\end{flushright}

\vspace{1em}
\hfill\today

We greatly appreciate the thorough comments from the editor and referees, and have made changes as requested. Below we detail our response to the referees' reports.

@@

\centerline{\textbf{Response to Referee 1}}

\begin{itemize}[parsep=1em,leftmargin=1em]

\item \comment{The authors spend an inadaquate amount of time discussing other approaches for solving this problem and comparing their methodology (e.g., closest point method, radial basis functions). What is the complexity convergence behavior of other approaches that can handle spherical caps?}

We have added in a discussion of the closest point method. We have chosen to omit discussion on radial basis functions as we are not aware of references that consider their usage on spherical caps.

### 2021-05-04 papers/spherical-caps/revised/spherical-caps.tex
response edits

Other boundary conditions beyond those already presented here are beyond the scope of this paper. However, the approach established for the case of a triangle domain in 2D shows how Neumann conditions can be done by writing these as a system of equations in partial derivatives \cite{olver2019triangle}. This approach may also work here for the spherical cap. Ideally, one would properly tackle the tangent space (which again is beyond the scope of this paper) which would lower the degrees of freedom.

>>>>

Other boundary conditions beyond those already presented here are beyond the scope of this paper. However, the approach established for the case of a triangle domain in 2D shows how Neumann conditions can be considered  as a system of equations in partial derivatives involving Dirchlet conditions \cite{olver2019triangle}. This approach may also work here for the spherical cap. Ideally, one would properly tackle the tangent space (which again is beyond the scope of this paper) which would lower the degrees of freedom.
